### 2021-10-19 paper/paper.tex
made clearer a claim I thought could be taken the wrong way

\vskip 6pt
Random testing also generates test cases, and we know, from Arcuri et~al, that these test cases increase code coverage with increasing numbers of test cases in a predictable way~\cite{Arcuri2012-az}. Random testing has the benefit that you can run it for an arbitrarily long time during acceptance testing. There is also no requirement that values be completely random within the domain of arguments. They are almost always biased towards values that carry risk, such as empty strings or other corner cases. Here, a preference for combinatorial interaction testing comes from a lack of test-running resources or from the ease of specifying sample argument values instead of the complete domain of the arguments.

>>>>

\vskip 6pt
Random testing also generates test cases, and we know, from Arcuri et~al, that these test cases increase code coverage with increasing numbers of test cases in a predictable way~\cite{Arcuri2012-az}. Random testing has the benefit that you can run it for an arbitrarily long time during acceptance testing. There is also no requirement that values be completely random within the domain of arguments. They are almost always biased towards values that carry risk, such as empty strings or other corner cases. Combinatorial interaction testing is preferable to random testing when there are few test-running resources.
